---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ukpolice
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/ukpolice?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/ukpolice)[![Travis-CI Build Status](https://travis-ci.org/njtierney/ukpolice.svg?branch=master)](https://travis-ci.org/njtierney/ukpolice)[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/ukpolice/master.svg)](https://codecov.io/github/njtierney/ukpolice?branch=master)

ukpolice is an R package that facilitates retrieving data from the [UK police database.](https://data.police.uk/)

The data provided by the API contains public sector information licensed under the [Open Government Licence v3.0.](http://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/)

# Installation

Install from GitHub

```{r install, eval = FALSE}

#install.packages("remotes")
remotes::install_github("njtierney/ukpolice")

```

# Usage

## Crime

`ukp_crime()` draws crimes from within a one mile radius of the location.

When no date is specified, it uses the latest month available, which can be found using `ukp_last_update()`.

```{r crime-example}
library(ukpolice)

crime_data <- ukp_crime(lat = 52.629729, lng = -1.131592)

head(crime_data)

ukp_last_update()

```

When date is specified, it must be in the format "YYYY-MM". Currently `ukp_crime()` only allows for searching of that current month.

```{r crime-data-date-example}

crime_data_date <- ukp_crime(lat = 52.629729, 
                             lng = -1.131592,
                             date = "2016-03")

head(crime_data_date)

```

This is still a little buggy at the moment as it returns blank columns for variables like `persistent_id` and `context`, `location_subtype`, and `outcome_status`. This issue is currently logged at [issue #11](https://github.com/njtierney/ukpolice/issues/11).

`ukp_crime_poly()` finds all crimes within the polygon provided by a dataframe with columns names "lat" and "long".

```{r crime-data-poly-example}

poly_df_3 <- data.frame(lat = c(52.268, 52.794, 52.130),
                        long = c(0.543, 0.238, 0.478))

poly_df_3

ukp_data_poly_3 <- ukp_crime_poly(poly_df_3)

head(ukp_data_poly_3)

```



## Neighbourhood

`ukp_neighbourhood()`, retrieves a list of neighbourhoods for a force, https://data.police.uk/docs/method/neighbourhoods/

This returns a tibble with columns `id` and `name`. 

```{r ukp-neighbourhood}

ukp_neighbourhood("leicestershire")

```

- `id` is a Police force specific team identifier, (note that this identifier is not unique and may also be used by a different force). 
- `name` is the name for the neighbourhood.

# Examples

## Explore the number of crime types

```{r count-example}

library(dplyr)
library(ggplot2)

crime_data <- ukp_crime(lat = 52.629729, lng = -1.131592)

crime_data %>%
  count(category) %>%
  ggplot(aes(x = reorder(category, n),
             y = n)) + 
  geom_col() + 
  labs(x = "Crime Type",
       y = "Number of Crimes",
       title = paste0("Crimes commited in ",crime_data_date$date[1])) +
  coord_flip() +
  theme_minimal()
  
```


## Use leaflet

You can add a popup that displays the crime type using the `popup` argument in leaflet.

```{r leaflet-example-popup}
library(leaflet)
crime_data <- ukp_crime(lat = 52.629729, lng = -1.131592)
crime_data %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(popup = ~category)

```


## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
