---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ukpolice
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/ukpolice?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/ukpolice)[![Travis-CI Build Status](https://travis-ci.org/njtierney/ukpolice.svg?branch=master)](https://travis-ci.org/njtierney/ukpolice)[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/ukpolice/master.svg)](https://codecov.io/github/njtierney/ukpolice?branch=master)

ukpolice is an R package that facilitates retrieving data from the [UK police database.](https://data.police.uk/)

This package is in a very beta stage, and I'm still learning a lot about APIs!

# Installation

Install from GitHub

```{r eval = FALSE}

#install.packages("devtools")
devtools::install_github("njtierney/ukpolice")

```

# Usage

`ukp_neighbourhood`, retrieves a list of neighbourhoods for a force, https://data.police.uk/docs/method/neighbourhoods/

This returns a tibble with columns `id` and `name`. 

```{r}

library(ukpolice)
ukp_neighbourhood("leicestershire")

```

- `id` is a Police force specific team identifier, (note that this identifier is not unique and may also be used by a different force). 
- `name` is the name for the neighbourhood.

`ukp_crime_street_point` draws crimes from within a one mile radius.

```{r}

ukp_crime_street_point(lat = 52.629729, lng = -1.131592)

```

This is still a little buggy at the moment as it returns blank columns, but this is a work in progress!

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
