---
title: "Getting started with ukpolice"
author: "Nicholas Tierney"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

ukpolice is an R package that facilitates retrieving data from the [UK police database.](https://data.police.uk/). The data provided by the API contains public sector information licensed under the [Open Government Licence v3.0.](http://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/)

# Get the crime data with `ukp_crime`

`ukp_crime()` draws crimes from within a one mile radius of the location.

```{r crime-example}
library(ukpolice)

crime_data <- ukp_crime(lat = 52.629729, lng = -1.131592)

head(crime_data)

```

When no date is specified, it uses the latest month available, which can be found using `ukp_last_update()`.

```{r ukp-last-update}

ukp_last_update()

```

## Specify a month and year for data

When date is specified, it must be in the format "YYYY-MM". Currently `ukp_crime()` only allows for searching of that current month.

```{r crime-data-date-example}

crime_data_date <- ukp_crime(lat = 52.629729, 
                             lng = -1.131592,
                             date = "2016-03")

head(crime_data_date)

```

This is still a little buggy at the moment as it returns blank columns for variables like `persistent_id` and `context`, `location_subtype`, and `outcome_status`. This issue is currently logged at [issue #11](https://github.com/njtierney/ukpolice/issues/11).

# Example usage

## Explore the number of crime types

```{r count-example}

library(dplyr)
library(ggplot2)

crime_data <- ukp_crime(lat = 52.629729, lng = -1.131592)

crime_data %>%
  count(category) %>%
  ggplot(aes(x = reorder(category, n),
             y = n)) + 
  geom_col() + 
  labs(x = "Crime Type",
       y = "Number of Crimes",
       title = paste0("Crimes commited in ",crime_data_date$date[1])) +
  coord_flip() +
  theme_minimal()
  
```

## Use leaflet

You can add a popup that displays the crime type using the `popup` argument in leaflet.

```{r leaflet-example-popup}
library(leaflet)
crime_data <- ukp_crime(lat = 52.629729, lng = -1.131592)
crime_data %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(popup = ~category)

```

# Get crime within a polygon

`ukp_crime_poly()` finds all crimes within the polygon provided by a dataframe with columns names "lat" and "long".

```{r crime-data-poly-example}

poly_df_3 <- data.frame(lat = c(52.268, 52.794, 52.130),
                        long = c(0.543, 0.238, 0.478))

poly_df_3

ukp_data_poly_3 <- ukp_crime_poly(poly_df_3)

head(ukp_data_poly_3)

```

# Neighbourhood information

`ukp_neighbourhood()`, retrieves a list of neighbourhoods for a force, https://data.police.uk/docs/method/neighbourhoods/

This returns a tibble with columns `id` and `name`. 

```{r ukp-neighbourhood}

ukp_neighbourhood("leicestershire")

```

- `id` is a Police force specific team identifier, (note that this identifier is not unique and may also be used by a different force). 
- `name` is the name for the neighbourhood.

